Staged Abstract Interpreters

### 2019-08-13 paper/70_eval.tex
revision

\paragraph{Implementation and Evaluation Environment}
We implement the abstract interpreters for control-flow analysis, i.e., a
value-flow analysis focus on lambda terms in functional languages. A front-end
desugars Scheme to a small core language that makes the analyzer easy to
implement. As described in Section \ref{cfa}, we implement two monovariant
0-CFA-like analysis, one is equipped with store-widening, the other does not.
We also implement several optimizations mentioned in Section \ref{staged_ds}.

We use Scala 2.12.8 and Oracle JVM 1.8.0-191, running on an Ubuntu 16.04 LTS
(kernel 4.4.0) machine. All of our evaluations were performed on a machine with 4 Intel
Xeon Platinum 8168 CPU at 2.7GHz and 3 TiB of RAM. Although the machine has 96
cores (192 threads) in total, the abstract interpreters are single-threaded.
To minimize the effect of warming-up from the JVM JIT compiler, all the
experiments are executed for 20 times and we report the statistical median value
of the running times. We set a 5 minutes timeout.

@@

>>>>

\paragraph{Implementation and Evaluation Environment}
We implement the abstract interpreters for control-flow analysis, i.e., a
value-flow analysis that computes which lambda terms can be called at each
call-sites in functional languages. With other suitable abstract domains, the
abstract interpreter also can be extended to other analyses. A front-end
desugars Scheme to a small core language that makes the analyzer easy to
implement. As described in Section \ref{cfa}, we implement two monovariant
0-CFA-like analysis, one is equipped with store-widening, the other does not.
\todo{why store widening?} Our prototype implementation currently generates
Scala code; the generated Scala code will be compiled and executed also on JVM.
it is possible to also generate C/C++ code in the future. In the experiments, we
implement several optimizations mentioned in Section \ref{staged_ds},
specifically, the selective caching and rewriting rules exploiting
partially-static data. These optimizations are useful to reduce the size of
generated code.

We use Scala 2.12.8 and Oracle JVM 1.8.0-191 \footnote{The options for running
  JVM is set to the following: \texttt{-Xms2G -Xmx8G -Xss1024M
  -XX:MaxMetaspaceSize=2G - XX:ReservedCodeCacheSize=2048M}}, running on an Ubuntu 16.04 LTS
(kernel 4.4.0) machine. All of our evaluations were performed on a machine with 4 Intel
Xeon Platinum 8168 CPU at 2.7GHz and 3 TiB of RAM. Although the machine has 96
cores (192 threads) in total, the abstract interpreters are single-threaded.
To minimize the effect of warming-up from the HotSpot JIT compiler, all the
experiments are executed for 20 times and we report the statistical median value
of the running times. We set a 5 minutes timeout.

@@

\todo{analyze some interesting examples}

### 2019-08-13 paper/80_related.tex
revision

\paragraph{Abstract Interpreters} Abstract interpretation was proposed as a
semantic-based approach to build sound static analysis by approximation
\cite{DBLP:conf/popl/CousotC77}. As semantic artifacts, the Abstracting Abstract
Machines (AAM) \cite{DBLP:journals/jfp/HornM12, DBLP:conf/icfp/HornM10} approach
shows that abstract interpreters can be derived systematically from concrete
semantic artifacts. The AAM approach is closely related to control-flow analysis
for higher-order languages \cite{Midtgaard:2012:CAF:2187671.2187672}.
Using monads to construct abstract interpreters is explored by
\citet{Sergey:2013:MAI:2491956.2491979} and
\citet{DBLP:journals/pacmpl/DaraisLNH17, Darais:2015:GTM:2814270.2814308}.
Similar to definitional abstract interpreters, \citet{Wei:2018:RAA:3243631.3236800}
reconstruct big-step abstract interpreters with delimited continuations;
\citet{Keidel:2018:CSP:3243631.3236767} present a modular arrow-based abstract
interpreter that makes proof of soundness can be constructed compositionally.
\citet{DBLP:conf/cc/CousotC02} proposed an abstract interpretation framework for
modular analysis. We borrow the notation of modular analysis, \todo{but intentional properties
  are different, compare with summary}

\paragraph{Two-level Semantics}

@@

\paragraph{Control-flow Analysis}

>>>>

\paragraph{Abstract Interpreters} Abstract interpretation was proposed as a
semantic-based approach to build sound static analysis by approximation
\cite{DBLP:conf/popl/CousotC77}. As to build semantic artifacts, the Abstracting
Abstract Machines (AAM) \cite{DBLP:journals/jfp/HornM12, DBLP:conf/icfp/HornM10}
approach shows that abstract interpreters can be derived systematically from concrete
semantic artifacts. The AAM approach is closely related to control-flow analysis
for higher-order languages \cite{Midtgaard:2012:CAF:2187671.2187672}.
Using monads to construct abstract interpreters is explored by
\citet{Sergey:2013:MAI:2491956.2491979} and
\citet{DBLP:journals/pacmpl/DaraisLNH17, Darais:2015:GTM:2814270.2814308}.
The unstaged abstract interpreter in this paper follows the abstracting definitional
interpreters approach from \citet{DBLP:journals/pacmpl/DaraisLNH17}.
Similar to definitional abstract interpreters, \citet{Wei:2018:RAA:3243631.3236800}
reconstruct big-step abstract interpreters with delimited continuations;
\citet{Keidel:2018:CSP:3243631.3236767} present a modular arrow-based abstract
interpreter that makes proof of soundness can be constructed compositionally.
\citet{DBLP:conf/cc/CousotC02} proposed an abstract interpretation framework for
modular analysis. We borrow the notation of modular analysis, \todo{but intentional properties
  are different, compare with summary}

\paragraph{Two-level Semantics} The idea of reinterpreting the semantics as
abstract interpretation can be traced to Nielson's two-level semantics
\cite{NIELSON1989117}; using two-level semantics for code generation was also
explored by \citet{NIELSON198859}. \citet{Sergey:2013:MAI:2491956.2491979}'s
work of monadic abstract interpreters is also closely related to the two-level
semantics: the use of a generic interface with monads and then reinterpret it by
different semantics is already two-level. Instead of focusing on semantics, this
paper shows how a staged analyzer can be built and used to increase efficieny of
static analysis, we augment the monadic abstract interpreter from another
dimension, using code generation to produce efficient low-level code.

@@

\paragraph{Control-flow Analysis} useful applications, why important
